Verifying Demonstrations

### 2018-02-28 paper/DB-anon-cred.tex
Clarifies PoPoK and DBPK

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 
proving \(\DBPK[\alpha][a = \alpha^2]\).
We, on the other hand, need \iac{DBPK} protocol for discrete logarithms.
We will now introduce such a protocol which will allow us to do \ac{DB} 
anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBIF} resistance --- \ie not \ac{DBTF} resistance.

>>>>

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge, instead of \ac{DBPK}.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 
proving \(\DBPK[\alpha][a = \alpha^2]\).
We, on the other hand, need \iac{DBPK} protocol for discrete logarithms.
We will now introduce such a protocol which will allow us to do \ac{DB} 
anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBIF} resistance --- \ie not \ac{DBTF} resistance.
